---
title: 'Quiz #7'
author: "Rachel Brow"
date: "11/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '~/Dropbox/PSCI338')
```

### Question #1
```{r}
library("foreign")
library(car)
library(lmtest)
library(sandwich)
Kaiser <- read.dta("RawData/31117492.DTA",convert.factors = TRUE)
```

```{r}
#Creating binary Pres approval
Kaiser$presapp <- NA
Kaiser$presapp[Kaiser$trumpapp == "Strongly approve"] = 1
Kaiser$presapp[Kaiser$trumpapp == "Somewhat approve"] = 1
Kaiser$presapp[Kaiser$trumpapp == "Somewhat disapprove"] = 0
Kaiser$presapp[Kaiser$trumpapp == "Strongly disapprove"] = 0
Kaiser$presapp[Kaiser$trumpapp == "Don't know"] = NA
Kaiser$presapp[Kaiser$trumpapp == "Refused"] = NA
```

```{r}
linMod <- lm(presapp~rsex+RECAGE5+racethn,data=Kaiser)
summary(linMod)
coeftest(linMod, vcov = vcovHC(linMod, type="HC1"))
```

```{r}
#Male: Highest approval
linMod1 <- lm(presapp~rsex,data=Kaiser)
Kaiser$rsex.num <- as.numeric(Kaiser$rsex)
newdata1 = Kaiser[which(Kaiser$rsex.num == 1), ]
fit1 = predict(linMod1, newdata = newdata1)
summary(fit1)[4]
```
Males were the most likely to approve of President Trump, at 48.39 predicted value. Males are generally more likely to support Trump/Republicans compared to females/other. 
Although the "Refused" category for sex was the highest approval (at 1), it was an outlier because only one person refused to tell their sex.
```{r}
#BLACK, NON-HISPANIC: Lowest approval
linMod3 <- lm(presapp~racethn,data=Kaiser)
Kaiser$racethn.num <- as.numeric(Kaiser$racethn)
newdata4 = Kaiser[which(Kaiser$racethn.num == 2), ]
fit4 = predict(linMod3, newdata = newdata4)
summary(fit4)[4]
```
Black, non-Hispanics were the least likely to approve of President Trump, at 12.25 predicted value. This makes sense, as President Trump/Republicans are the least popular among black Americans compared to other racial groups.