---
title: 'Problem Set #2'
author: "Rachel Brow"
date: "9/12/2020"
output: html_document
---


## Question 1
Causal Theory: Access to arms promotes violent crime.

Hypothesis: A greater access to firearms leads to an increase in violence, especially in areas with higher levels of instability like the U.S.-Mexico border. 

Empirical Test: The researchers focused specifically on the 2004 expiration of the U.S. Federal Assault Weapons Ban and studied levels of homicide in municipalities of Mexico near the U.S.-Mexico Border.

Maintained assumptions: Guns are the most likely weapon in homicides and violent crimes. 

Measurement assumptions: violence= gun homicides
ports of entry on border= 2 border crossings > 20 miles apart


## 2.6 Practice Problems

##### #1
```{r, include=FALSE}
library("foreign")
library(car)
hanmerKalkanANES <- read.dta("RawData/hanmerKalkanANES.dta")
```

```{r}
# a.
ls(hanmerKalkanANES)
```

```{r}
# b.
head(hanmerKalkanANES)
```

```{r}
# c.
fix(hanmerKalkanANES)
```

##### #2
```{r}
summary(hanmerKalkanANES)
```
You can learn the mean, median, and quartiles of each variable in the data set. There are 617 missing observations. 

##### #3
```{r}
# a.
hanmerKalkanANES.trim <- na.omit(hanmerKalkanANES)
summary(hanmerKalkanANES.trim)
```
383 observations remain.

```{r}
# b.
hanmerKalkanANES.subset1 <- subset(hanmerKalkanANES, select = c(caseid, retecon, bushiraq))
summary(hanmerKalkanANES.subset1)
```

##### #4
```{r}
# a.
hanmerKalkanANES$partyid.dem <- as.numeric(hanmerKalkanANES$partyid<3)
summary(hanmerKalkanANES$partyid.dem)
hanmerKalkanANES$partyid.rep <- as.numeric(hanmerKalkanANES$partyid>3)
summary(hanmerKalkanANES$partyid.rep)
```

```{r}
# b.
hanmerKalkanANES$age <- (hanmerKalkanANES$age)^2
summary(hanmerKalkanANES$age)
```

```{r}
# c. 
hanmerKalkanANES$income.one <- recode(hanmerKalkanANES$income, "1:12=1;13:17=2;18:20=3;21:23=4")
table(hanmerKalkanANES$income.one)
```