---
title: 'Problem Set #1'
author: "Rachel Brow"
date: "9/6/2020"
output: html_document
---
## Question 1:

Causal theory: Women political leaders are more likely than men political leaders to engage in and maintain diplomatic relations due to higher empathy and conscientiousness.

Hypothesis: Women political leaders initiate more diplomatic visits to    foreign nations than men political leaders.
  
Possible Empirical Test: Compare women and men leaders of similar power and influence (e.g. both advanced democracies in the OECD) on the average number of initiated diplomatic visits per year. 

## 1.6 Practice Problems

#### 1:

```{r, echo = TRUE, eval = T,warning=FALSE}
 -7*2^3
 8/(8^2+1)
cos(pi)
sqrt(81)
log10(exp(4))
```


#### 2:

The command cor calculates the correlation coefficient of x and y if they are vectors.


#### 3:

The command runif generates random deviates from a uniform distribution on an interval from min to max.


#### 4:

```{r, echo=T, results='hide', warning=F}
x <- rnorm(1000)
y <- rnorm(1000)
cor(x,y)
```
```{r, echo=FALSE, warning=FALSE}
cat("The correlation coefficient of vectors x and y is", cor(x,y), "\n")
```


#### 5:

The package stringr has four main functions: character manipulation, whitespace tools, locale-sensitive operations, and pattern matching. I might want to use this package when creating an RMarkdown file, because I can manipulate the whitespace to format and organize the document.


