---
title: 'Problem Set #4'
author: "Rachel Brow"
date: "9/26/2020"
output: html_document
---

```{r setup, echo=FALSE}
knitr::opts_knit$set(root.dir = '~/Dropbox/PSCI338')
```

#### Question #1

##### a.
```{r}
# Probability of rolling any number on dice 1:
pr_dice1 <- 1/13
# Probability of rolling any number on dice 2:
pr_dice2 <- 1/13
# Probability of rolling a pair of 1's on dice 1 and dice 2:
pr_1 <- pr_dice1 * pr_dice2
# Probability of rolling two dice of the same number:
13 * pr_1
```

##### b.
```{r}
pr_eleven2 <- 9 * pr_1
9 * pr_1
```

##### c.
```{r}
pr_ten2 <- 1-pr_eleven2
1-pr_eleven2
```

##### d.
```{r}
pr_eleven1 <- 3 * pr_dice1
pr_ten1 <- 10 * pr_dice2
pr_eleven1 * pr_ten1
```

#### Question #2

##### a.
```{r}
1 * 3/51
```

##### b.
```{r}
pr_facecard1 <- 12/52
pr_facecard2 <- 11/51
pr_facecard1 * pr_facecard2
```

##### c.
```{r}
round((1-pr_facecard1) * (39/51),3)
```

##### d.
```{r}
pr_facecard1 * (40/51)
```

#### Question #3
Question 1 was dealing with two independent events (rolling dice), whereas Question 2 was dealing with 2 dependent events (drawing cards from a deck). In Question 2, the probability of drawing the second card depends on the probability of drawing the first.

#### Question #4

```{r}
pr_blue_box1 <- 3/5
pr_blue_box2 <- 2/7
pr_box1=pr_box2=1/2
pr_blue_and_box1 <- pr_blue_box1 * pr_box1
pr_blue_and_box2 <- pr_blue_box2 * pr_box2
pr_blue <- pr_blue_and_box1 + pr_blue_and_box2
# Probability that the coin came up heads given that she chose blue
pr_box1_blue <- pr_blue_and_box1/pr_blue
print(pr_box1_blue)
```

#### Question #5

```{r}
pr_tails <- 1/3
pr_heads <- 1/2
pr_tails_and_heads<- pr_tails * pr_heads
# Probability that the other side of a coin is tails given heads
pr_tails_heads <- pr_tails_and_heads/pr_heads
print(pr_tails_heads)
```

#### Question #6
Suppose that we ran a political poll that surveyed people in Massachusetts, Pennsylvania, and Texas. We got 300 responses from Texas, 200 responses from Pennsylvania, and 100 responses from Massachusetts. In Texas, 2/5 of the respondents identified as Democrats. In Pennsylvania, 1/2 of the respondents identified as Democrats. In Massachusetts, 3/5 of the respondents identified as Democrats. What is the probability thata respondent is from Texas given that he or she identified as a Democrat?
```{r}
# Given information:
pr_tx <- 1/2
pr_dem_tx <- 2/5
pr_pa <- 1/3
pr_dem_pa <- 1/2
pr_ma <- 1/6
pr_dem_ma <- 3/5
# Probability of Texas given a Democrat:
pr_tx_and_dem <- pr_tx * pr_dem_tx
pr_dem_and_nottx <- (pr_pa * pr_dem_pa) + (pr_ma * pr_dem_ma)
pr_dem <- pr_tx_and_dem + pr_dem_and_nottx
pr_tx_dem <- pr_tx_and_dem/pr_dem
print(pr_tx_dem)
```

#### Question #7

```{r} 
D <- 0.03
ND <- 0.97
positiveD <- 0.95
negativeD <- 0.05
positiveND <- 0.0015
negativeND <- 0.9995
# Calculate P(Disease|positive)
print((positiveD*D)/((positiveD*D)+(positiveND*ND)))
```

#### Question #8

```{r}
D <- 0.021
ND <- 0.989
positiveD <- 0.95
negativeD <- 0.05
positiveND <- 0.02
negativeND <- 0.98
# Calculate P(Disease|positive)
(positiveD*D)/((positiveD*D)+(positiveND*ND))
```